Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-09-12 Ben_Manuscripts/structure_paper/Draft.tex
Addition of quenched disorder discussion to draft with attempted minimization of flow disruption

  \subsubsection{\textit{Ionic conductivity calculations}}

@@

  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment because
  monomers in the simulated system stack further apart than those in the experimental
  system (Table~\ref{table:correlation_length}). We calculated $z$-direction pair distribution
  functions, $g(z)$, as described in Section~\ref{section:correlation_length}.
  %BJC11: Below is in methods but might be worth restating here? 
  %MRS12: no, OK here.
%  based on the center of mass of each monomer head group. In order
%  to calculate $g(z)$, we averaged all $z$-slices of the 3D pair distribution function, $g(x, y, z)$, 
%  (Equation~\ref{eqn:correlation}) within
%  2.1 \AA~of $g(0, 0, z)$. In this way we are measuring correlation between head 
%  groups within the same column. 
  The resulting distributions are generally characterized by decaying
  oscillatory behavior where the average distance between peaks corresponds to
  the average distance between stacked monomer head groups
  (Figure~\ref{fig:correlation}).  We calculated this equilibrated vertical
  stacking distance, $\mathit{d}_{equil}$, between monomers using
  Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked monomers is
  greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
  basins at the high part of that range and are on average 0.2 and 0.3 \AA~more
  distant. This behavior is
  not surprising since GAFF models atoms as point charges and  % BJC11: need reference %MRS12: just cite the GAFF paper.
  does not appropriately model the aromatic $\pi-\pi$ interactions, which would make
  it more energetically favorable for the monomers to stack closer together.  It
  is also possible that the tails prevent close stacking of monomer head groups
  and we do not achieve the timescales necessary for them to rearrange into a
  necessarily more tightly packed configuration. However, we equilibrated the
  system at 500 K then annealed it to 300 K in an attempt to coerce the tails into
  a more tightly packed configuration, however we saw no improvement in packing
  distance over our 300 K models. See section S-TBD for details.

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
	  $theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
	  we double the disorder (Noise factor = 2), the FWHM decreases by
	  51\%.}\label{fig:qy_fwhm}
  \end{figure}

  We can explain the discrepancies between R-$\pi$ seen experimentally
  and in simulation using what we have shown in this section. The stacking
  distance between monomer head groups is too large, likely due to failures
  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
  ordering in the $z$-direction in addition to high degrees of correlation 
  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
  which is also likely a consequence of columns that are too highly correlated.

  % BJC15 : Matt comment: "I found the discussion of pore structure in the first 
  % full paragraph on page 38 is a bit hard to follow. Maybe a schematic of what 
  % “in between sandwiched and parallel displaced” looks like would be helpful"
  The architecture of each column is therefore likely in between our sandwiched and parallel
  displaced configurations. The parallel displaced configuration that we have simulated in this
  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
  stacking mode. The experimental WAXS pattern shows faint off-axis features at the
  same $q_r$ value as R-double which is only present in simulated patterns generated from
  parallel displaced configurations. The monomers may prefer to be parallel displaced, but
  their displacement is likely only slightly shifted, on the $xy$ plane, from the
  center of mass of their vertically adjacent neighbors. In this way, columns can
  more easily act independently while maintaining a parallel displaced structure.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_36.eps}
  \caption{}\label{fig:pd_36}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_lt36.eps}
  \caption{}\label{fig:pd_lt36}
  \end{subfigure}
  \caption{Head groups are likely stack in a configuration between sandwiched and
  parallel displaced. (a) In our parallel displaced configurations with 5 monomers 
  per columns, we placed head groups so the angle, $\theta$, between vectors extending
  from vertically stacked head groups to the pore center equals 36$\degree$ 
  ((360$\degree$ / $ncol$) / 2 where $ncol$ is the number of columns per pore). 
  (b) In the true configuration, $\theta$ is likely between 0$\degree$ and 36 $\degree$.
  When $\theta$=0$\degree$, the system architecture is the same as a sandwiched 
  configuration.}\label{fig:between_pd}
  \end{figure}

@@

  Since the dynamics of this system appear to be quite slow, we can learn more about
  their time-averaged structure by studying ensembles of simulations.
  Disorder among head groups in the simulated atomistic systems is largely determined
  by each system's quenched configuration. We observe rapid reorganization of our 
  initial configurations into configurations with quenched disorder that does not
  vary significantly for the remainder of the % BJC15: I could quantify this more and put in supporting info
  simulation time. For that reason, we created ensembles of 40 simulations in both
  the parallel displaced and sandwiched configurations. We used the same equilibration
  technique as above (see section~\ref{section:equilibration}), however we stopped 
  the equilibration after 5 ns of unrestrained simulation. We simulated XRD patterns
  from the 40 concatenated trajectories. The $q_r$ cross-sections generated from the 
  two concatenated trajectories are shown in Figure~\ref{fig:ensemble_XRD}. 
  Qualitatively, the $q_r$ cross-sections of R-$\pi$ are nearly smooth, with small
  spikes near $q_r$=0. The data suggests that the average
  intensity of R-$\pi$ in sandwiched systems is about 3$\times$ higher than that in the
  parallel displaced configuration. Overall, the intensity of R-$\pi$ generated from the
  parallel displaced ensemble shows the best agreement with experiment so far. For
  simplicity, we will limit the following discussion to the parallel displaced 
  configuration. Equivalent data is available for the sandwiched configuration in the
  supporting information.
  %BJC15: limiting discussion to parallel displaced since it seems most consistent with experiment
  % However, I can switch it sandwiched very easily.

  %BJC15: This figure might not be necessary. Do the comparisons of emperical
  % cumulative distribution functions make the same point? 
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.png}
  \caption{Sandwiched}\label{fig:sandwiched_ensemble_rsection}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_rsection.png}
  \caption{Parallel Displaced}\label{fig:offset_ensemble_rsection}
  \end{subfigure}
  \caption{The $q_r$ section of R-$\pi$ is much smoother when simulated XRD patterns
  		   are generated from an ensemble of 40 independent simulations. The maximum 
  		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
  		   than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
  \end{figure}

  Independent simulations exhibit similar amounts of quenched disorder. For 
  each, we measured the deviation of the head group centers of mass from their
  idealized positions (see section~\ref{method:simple_systems}). 
  We created histograms of the standard deviations of each distribution which
  are shown in Figure~\ref{fig:ensemble_stds}. The distributions of standard deviations
  are fairly tight with ($\sigma_\sigma_z$, $\sigma_\sigma_r$, $\sigma_\sigma_\theta$) = (0.011 nm, 
  0.007 nm , 0.022 radians). We pooled the deviations from idealized positions 
  from all independent simulations in order to create the distributions shown in 
  Figure~\ref{fig:offset_ensemble_pooled}. The distributions appear 
  symmetric meaning that there is an equal chance for a head group to displace
  in the positive or negative $z$, $r$ or $\theta$-direction. We verified that
  this is the case for individual center of masses. 
  % For a given system, there are 400 head groups. 
  If we consider the center of mass of the first head group, we expect that the
  distribution of its deviation from its idealized position among all the 
  independent simulations
%  the $z$, $r$, and $\theta$ directions 
  should be symmetric about its idealized position. We can calculate the 
  empirical cumulative distribution function (ECDF) 
  of this distribution of deviations. 
  % Each ECDF contains 40 data points, one from each independent simulation.
  The ECDFs of 5 randomly selected centers of 
  mass are shown in Figure~\ref{fig:offset_ecdfs} (colored lines). We also calculated 
  the ECDF from the full distributions in Figure~\ref{fig:offset_ensemble_pooled}
  (black line with error bars). We generated error bars that represent the 95\% 
  confidence intervals, by randomly sampling 40 values (the same as the number 
  of independent simulations) from the distributions in 
  Figure~\ref{fig:offset_ensemble_pooled}, then measuring the deviation between
  the sampled ECDF and the full ECDF. The center of mass ECDFs lie between the
  error bars of the full ECDF within reason. This provides further evidence that
  each center of mass moves independently, in random directions when systems
  quench.

% Sandwiched: (0.019 nm, 0.007 nm, 0.023 radians)

  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{sandwiched_ensemble_stds.png}
%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_stds.png}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=0.45\textwidth]{offset_ensemble_stds.png}
%  \caption{Parallel Displaced}\label{fig:offset_ensemble_stds.png}
%  \end{subfigure}
  \caption{There is a narrow spread in the standard deviation of
  quenched disorder for each independent configuration.}\label{fig:ensemble_stds}
  \end{figure}

  %BJC15: will not waste much time formatting until we converge on a figure 
  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{\textwidth}
%  \includegraphics[width=\textwidth]{sandwiched_ensemble_pooled.png}
%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_pooled.png}
%  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_pooled.png}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ecdfs.png}
  \caption{Emperical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
  \caption{Radial density of select monomer components.}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{The distributions of the deviations of head group center of masses
  from their idealized positions generated using pooled data from all
  frames of each independent configuration is symmetric. This implies that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction.}\label{fig:full_ensemble_distributions}
  \end{figure}

@@

  %BJC6: not sure if this should go in supplemental
%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.4\textwidth}
%	  \includegraphics[width=\linewidth]{sandwich_rzplot_highlimit_cbar.png}
%	  \caption{}\label{fig:simulated_adjusted_colorbar}
%  \end{subfigure}
%  \begin{subfigure}{0.4\textwidth}
%	  \includegraphics[width=\linewidth]{WAXS_raw_adjusted_colorbar.png}
%	  \caption{}\label{fig:experimental_adjusted_colorbar}
%  \end{subfigure}
%  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections in 
%  the simulated diffraction patterns (a). Here, the colorbar was scaled so that the max is 6x
%  higher than all other plots.}\label{fig:intense_rpi}
%  \end{figure}

>>>>

  \subsection{\textit{Ionic conductivity calculations}}

@@

  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment because
  monomers in the simulated system stack further apart than those in the experimental
  system (Table~\ref{table:correlation_length}). We calculated $z$-direction pair distribution
  functions, $g(z)$, as described in Section~\ref{section:correlation_length}.
  %BJC11: Below is in methods but might be worth restating here? 
  %MRS12: no, OK here.
%  based on the center of mass of each monomer head group. In order
%  to calculate $g(z)$, we averaged all $z$-slices of the 3D pair distribution function, $g(x, y, z)$, 
%  (Equation~\ref{eqn:correlation}) within
%  2.1 \AA~of $g(0, 0, z)$. In this way we are measuring correlation between head 
%  groups within the same column. 
  The resulting distributions are generally characterized by decaying
  oscillatory behavior where the average distance between peaks corresponds to
  the average distance between stacked monomer head groups
  (Figure~\ref{fig:correlation}).  We calculated this equilibrated vertical
  stacking distance, $\mathit{d}_{equil}$, between monomers using
  Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked monomers is
  greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
  basins at the high part of that range and are on average 0.2 and 0.3 \AA~more
  distant. This behavior is
  not surprising since GAFF models atoms as point charges and  % BJC11: need reference %MRS12: just cite the GAFF paper.
  does not appropriately model the aromatic $\pi-\pi$ interactions, which would make
  it more energetically favorable for the monomers to stack closer together.  It
  is also possible that the tails prevent close stacking of monomer head groups
  and we do not achieve the timescales necessary for them to rearrange into a
  necessarily more tightly packed configuration. However, we equilibrated the
  system at 500 K then annealed it to 300 K in an attempt to coerce the tails into
  a more tightly packed configuration, but we saw no improvement in packing
  distance over our 300 K models. See section S-TBD for details.

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
	  we double the disorder (Noise factor = 2), the FWHM decreases by
	  51\%.}\label{fig:qy_fwhm}
  \end{figure}

@@

  Since the dynamics of this system appear to be quite slow, and consequently most of
  our analysis has been focused on a small set of quenched configurations whose 
  structures do not vary significantly with time, we attempted
  to learn more about their time-averaged structures by studying ensembles of simulations.
%  Disorder among head groups in the simulated atomistic systems is largely determined
%  by each system's quenched configuration. We observe rapid reorganization of our 
%  initial configurations into configurations with quenched disorder that does not
%  vary significantly for the remainder of the
%  simulation time. For that reason, 
  We created ensembles of 40 simulations in both the parallel displaced and 
  sandwiched configurations. We used the same equilibration technique as above 
  (see section~\ref{section:equilibration}), however we built the initial
  configurations with randomly displaced columns in the $z$-direction and
  then stopped their equilibration after 5 ns of unrestrained simulation. We 
  simulated XRD patterns from the 40 concatenated trajectories. The $q_r$ 
  cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
  in Figure~\ref{fig:ensemble_XRD}. Qualitatively, the cross-sections
  of are nearly smooth, with small spikes near $q_r$=0. The data 
  suggests that the average intensity of R-$\pi$ in sandwiched systems is 
  about 3$\times$ higher than that in the parallel displaced configuration. 
  Overall, the intensity of R-$\pi$ generated from the parallel displaced 
  ensemble shows the best agreement with experiment so far. For simplicity, 
  we will limit the following discussion to the parallel displaced configuration.
  Equivalent data is available for the sandwiched configuration in the
  supporting information. %BJC15: to be added
  %BJC15: limiting discussion to parallel displaced since it seems most consistent with experiment
  % However, I can switch it to sandwiched very easily. The discussion below will remain the same

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.png}
  \caption{Sandwiched}\label{fig:sandwiched_ensemble_rsection}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_rsection.png}
  \caption{Parallel Displaced}\label{fig:offset_ensemble_rsection}
  \end{subfigure}
  \caption{The $q_r$ section of R-$\pi$ is much smoother when we generate simulated XRD
  		   patterns from an ensemble of 40 independent simulations. The maximum 
  		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
  		   than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
  \end{figure}

  Independent simulations exhibit similar amounts of quenched disorder. 
  We pooled the deviations of each head group COM from idealized positions
  from all independent simulations in order to create the distributions shown in 
  Figure~\ref{fig:offset_ensemble_pooled} 
  (see section~\ref{method:simple_systems}). The distributions appear 
  symmetric meaning that there is an equal chance for a head group to displace
  in the positive or negative $z$, $r$ or $\theta$-direction. We verified that
  this is the case for individual COMs. 
  % For a given system, there are 400 head groups. 
  If we consider the COM of a given head group, we expect that the
  distribution of its deviations from its idealized position among all the 
  independent simulations
%  the $z$, $r$, and $\theta$ directions 
  should be symmetric about its idealized position. We can calculate the 
  empirical cumulative distribution function (ECDF) 
  of these distributions of deviations. 
  % Each ECDF contains 40 data points, one from each independent simulation.
  The ECDFs of 3 randomly selected COMs
  are shown in Figure~\ref{fig:offset_ecdfs} (colored lines). The average 
  of all COM ECDFs is represented by the red line with the 95 \% confidence
  interval represented by the red error bars. We also calculated 
  the ECDF from the full distributions in Figure~\ref{fig:offset_ensemble_pooled}
  (black line with error bars). We generated error bars that represent the 95\% 
  confidence intervals, by performing 1000 trials where we randomly sampled 40
  values (the same as the number of independent simulations) from the distributions in 
  Figure~\ref{fig:offset_ensemble_pooled}, then measured the deviation between
  the sampled ECDF and the full ECDF. These error bars are generally smaller than
  those generated from the 400 COM ECDFs. This is because there is a wider
  distribution of mean COM deviations than the mean deviations from distributions
  sampled from the full distribution. The above evidence supports that each quenched
  configuration is random and mostly independent.

  %BJC15: will not waste much time formatting until we converge on a figure 
  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{\textwidth}
%  \includegraphics[width=\textwidth]{sandwiched_ensemble_pooled.png}
%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_pooled.png}
%  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_pooled.png}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  % BJC15: I don't think it's necessary to put the 3 randomly selected ECDFs in since it
  % doesn't provide extra information and clutters the figure. Left there for now.
  % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
  \includegraphics[width=\textwidth]{offset_ecdfs.png}
  \caption{Empirical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \caption{(a) The distributions of the head group COM deviations
  from their idealized positions generated using pooled data from all
  frames of each independent configuration is symmetric. This implies that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
  given head group is displaced randomly upon quenching. The ECDF generated from
  the pooled distributions (black) in (a) agree with the means of the 
  ECDFs generated from each COM (red). The red error bars are larger than
  the black error bars since there is a wider distribution of mean COM
  deviations than the mean deviations of distributions sampled from the full
  distribution.}\label{fig:full_ensemble_distributions}
  \end{figure}

  % BJC15: How important is it to prove in the main text (rather than supporting)
  % that the long systems sample the same distribution as above. Since they were
  % generated using the same procedure, why should the reader question it?

  The systems that we ran for 400 ns and used for most of our analysis are
  representative of the long term simulation behavior of any system chosen from the 
  ensemble. The distributions of standard deviations generated from each of
  the ensemble trajectories (Figures~\ref{fig:offset_ensemble_stds} 
  and~\ref{fig:offset_ensemble_means}) are fairly tight with ($\sigma_{\sigma_z}$,
  $\sigma_{\sigma_r}$, $\sigma_{\sigma_\theta}$) = (0.011 nm, 0.007 nm , 0.022 radians).
  We analyzed the first 5 ns of the 400 ns ordered parallel displaced
  configuration and observe the same amount of disorder (based on the $\sigma$ values
  in Figure~\ref{fig:offset_ensemble_stds}) with indistinguishable 
  mean values. Additionally, we calculated the radial density of monomer components as a 
  function of their distance from the pore centers (Figure~\ref{fig:offset_ensemble_regional_density}).
  All simulations have similar profiles. The distribution of sodium ions near the
  pore center is relatively noisy since the sodium ions are have much more 
  translational freedom than the head groups.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_stds.png}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_means.png}
  \caption{}\label{fig:offset_ensemble_means}
  % BJC15: The mean z-value seems a little silly since it is basically zero except for numerical error I presume
  % The mean is required to be zero for the calculation to work since columns are randomly displaced.
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
  %BJC15: I can explicitly define the colors for each system since all the ugly colors come out on top
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered parallel displaced system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $z$, $r$ and $\theta$ from the first 5 ns of the main
  system (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}

  We can explain the discrepancies between R-$\pi$ seen experimentally
  and in simulation using what we have shown in this section. The stacking
  distance between monomer head groups is too large, likely due to failures
  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
  ordering in the $z$-direction in addition to high degrees of correlation 
  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
  which is also likely a consequence of columns that are too highly correlated.
  If we limit ourselves to standard simulation techniques, it is necessary to 
  average data generated from ensembles of independent simulation trajectories
  in order to begin converging on time-averaged descriptions of the system's
  molecular structure.

  % BJC15 : Matt comment: "I found the discussion of pore structure in the first 
  % full paragraph on page 38 is a bit hard to follow. Maybe a schematic of what 
  % “in between sandwiched and parallel displaced” looks like would be helpful"
  % BJC15: could move figure to supplemental to save space
  % BJC15: Added a transition type clause to the beginning of this first sentence
  % to help with flow. It might be too much though.
  A secondary conclusion that we've drawn from the evidence in this section is 
  that the architecture of each column is likely in between our sandwiched
  and parallel displaced configurations. The parallel displaced configuration 
  that we have simulated in this paper is an exaggerated manifestation of the 
  parallel displaced $\pi-\pi$ stacking mode. Not only is the intensity of R-$\pi$
  calculated from the ensemble of parallel displaced simulations in close agreement
  with experiment, but the experimental WAXS pattern shows faint off-axis features
  at the same $q_r$ value as R-double which are only present in simulated patterns
  generated from parallel displaced configurations. The monomers may prefer to be
  parallel displaced, but their displacement is likely only slightly shifted, on 
  the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
  (See Figure~\ref{fig:between_pd}). In this way, columns can more easily act 
  independently while maintaining a parallel displaced structure. It is hard to
  imagine parallel displaced columns, as we have set them up, acting independently 
  unless we force them to be that way, as we did to create the ensemble of parallel
  displaced simulations.

  %BJC15: figure in response to Matt
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_36.eps}
  \caption{}\label{fig:pd_36}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_lt36.eps}
  \caption{}\label{fig:pd_lt36}
  \end{subfigure}
  \caption{Head groups are likely stack in a configuration between sandwiched and
  parallel displaced. (a) In our parallel displaced configurations with 5 monomers 
  per columns, we placed head groups so the angle, $\theta$, between vectors extending
  from vertically stacked head groups to the pore center equals 36$\degree$ 
  ((360$\degree$ / $ncol$) / 2 where $ncol$ is the number of columns per pore). 
  (b) In the true configuration, $\theta$ is likely between 0$\degree$ and 36 $\degree$.
  When $\theta$=0$\degree$, the system architecture is the same as a sandwiched 
  configuration.}\label{fig:between_pd}
  \end{figure}

@@
